---
title: "Titanic ggplot2 Exrercise"
author: "Sean F. Larsen"
date: "May 22, 2019"
output: html_document
---

## Data Visualization with ggplot2 (Part 1) - Final Excersize

This is the ggplot code for the final excercize of the ggplot2 (part 1) course.
The code is plotting data from a condensed Titanic dataset of 714 observations and 4 variable.
Using a Titanic dataset from a presvious excersise, the four variables were saved into a CSV file.
No observations were deleted.

This dataset will be used for this excersise.

```{r echo=TRUE}
library(ggplot2)
titanic <- read.csv(file="titanic_exercise.csv", header=TRUE, sep = ",")
```

## Including Plots

This is the code from the excersize:

```{r echo=TRUE}
# 1 - Check the structure of titanic
str(titanic)

# 2 - Use ggplot() for the first instruction
ggplot(titanic, aes(x = pclass, fill = sex)) + geom_bar(position = "dodge")

# 3 - Plot 2, add facet_grid() layer
ggplot(titanic, aes(x = pclass, fill = sex)) + geom_bar(position = "dodge") + facet_grid(. ~ survived)

# 4 - Define an object for position jitterdodge, to use below
posn.jd <- position_jitterdodge(0.5, 0, 0.6)

# 5 - Plot 3, but use the position object from instruction 4
ggplot(titanic, aes(x = pclass, y = age, col = sex)) + geom_point(position = posn.jd, size = 3, alpha = 0.5) + facet_grid(. ~ survived)
```
